Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-02-05 paper/paper.tex
changed result of stability analysis Tested everything on node32.

In order to explain this theoretically, we have performed stability
analysis of the five differential equations in an infinite slab that
shows a characteristic half wavelength in perturbative spatial
oscillations at which the system becomes unstable.  This length is
dependent upon slab thickness as shown in
Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
widths of our simulated flattened cells, the steady, two pole
oscillations seem to break down when the the shortest distance across
the cell is approximately equal to the characteristic half wavelength
at the particular thickness at which we simulate (our simulations of
cells with thickness $0.25\mu m$ corresponds to half wavelengths of
\fixme{check next number} $1.91\mu m$).  Huang~\cite{huang2003dynamic}
performs a similar analysis for a cylindrical shape and finds
characteristic half wavelengths of $2\mu m$.

>>>>

In order to explain this theoretically, we have performed stability
analysis of the five differential equations in an infinite slab that
shows a characteristic half wavelength in perturbative spatial
oscillations at which the system becomes unstable.  This length is
dependent upon slab thickness as shown in
Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
widths of our simulated flattened cells, the steady, two pole
oscillations seem to break down when the the shortest distance across
the cell is approximately equal to the characteristic half wavelength
at the particular thickness at which we simulate (our simulations of
cells with thickness $0.25\mu m$ corresponds to half wavelengths of
$2.13\mu m$).  Huang~\cite{huang2003dynamic} performs a similar
analysis for a cylindrical shape and finds characteristic half
wavelengths of $2\mu m$.
